Columnar VCF for Biobank scale datasets using Zarr

### 2024-04-15 paper.tex
DivBrowse
Closes #3

OME-Zarr~\cite{rzepka2023toward}
ITS\_LIVE ice velocity dataset~\citep{fahnestock2023mappin} using 
the Zarr.js Javascript interface to visualise the ``massive''
dataset [how big is it?]

@@

Spatial Omics:
emObject~\citep{baker2023emobject}
SpatialData~\citep{marconato2024spatialdata}

>>>>

ITS\_LIVE ice velocity dataset~\citep{fahnestock2023mappin} using 
the Zarr.js Javascript interface to visualise the ``massive''
dataset [how big is it?]

@@

Spatially resolved omics data~\citep{baker2023emobject,marconato2024spatialdata}
building on the Zarr-based OME-NGFF format~\citep{moore2023ome,rzepka2023toward}

DivBrowse~\citep{konig2023divbrowse}. Works with VCF data using 
the scikit-allel \texttt{vcf\_to\_zarr} function, (produces 
a precursor to the VCF-Zarr specification here). It's a 
browser, using Zarr as the storage backend.
